\section{Introduction}
\label{sec:introduction}

Generative artificial intelligence is widely expected to be the defining labor-market shock of the 2020s. The launch of ChatGPT on 30 November 2022 gave the world's first general-purpose large language model (LLM) to hundreds of millions of users within months, and occupational exposure measures suggest that roughly half of US jobs have at least one task that LLMs can perform twice as fast as a human \citep{Eloundou2023_gpt_exposure}. Against these projections, the first set of careful causal estimates is striking. \citet{HumlumVestergaard2025_llm} use Danish administrative data linked to a 100{,}000-worker adoption survey and rule out wage and hours effects larger than two percent, two years after launch. Two-percent effects are economically small. They are also geographically narrow: essentially every credible causal estimate of how LLMs have reshaped aggregate labor markets comes from the United States, Denmark, or online freelance platforms in which workers in advanced economies dominate.

This leaves the first-order question -- whether the most widely hyped general-purpose technology of the decade has actually moved labor-market outcomes -- essentially unresolved for the developing world. Latin America is the natural place to ask. The region's aggregate informality rate sits near 55 percent, with country-specific rates between 25 percent in Uruguay and more than 70 percent in parts of the Andean region. Formal and informal workers occupy segmented markets with different wage-setting institutions, different degrees of exposure to digital technology, and different buffers against productivity shocks. Exposure to LLMs in Latin America is also structurally different: \citet{Azuara2024_idb_ai} show that predicted exposure tilts sharply toward formal, female, urban, and tertiary-educated workers in Chile, Mexico, and Peru, and \citet{Ciaschi2025_distributive_ai} and \citet{EganadelSol2025_ai_lac} extend this exposure-only picture to the broader region. What no existing paper provides is a causal estimate of whether this exposure has translated into actual labor-market responses.

This paper fills that gap. I assemble harmonized labor force surveys for seven Latin American countries (Chile, Colombia, Costa Rica, Ecuador, Mexico, Peru, and Uruguay) covering 2021Q1 through 2025Q4, map the complementary-exposure score $\beta$ of \citet{Eloundou2023_gpt_exposure} from SOC-2010 to ISCO-08 via the BLS crosswalk (match rate 98.2 percent at the 4-digit level), and estimate the Average Causal Response on the Treated (ACRT) along the continuous exposure dimension using the difference-in-differences estimator of \citet{CallawayCGBS2024_continuous}. The empirical strategy is run \emph{country by country}: each of the seven countries delivers its own estimate $\hat\tau^c$, its own pre-trend test, its own Honest-DiD breakdown bound, and its own formality decomposition. The headline result is the side-by-side comparison of the seven $\hat\tau^c$ values rather than a pooled coefficient. I use $\beta$ rather than the upper-bound score $\zeta$ because $\beta$ captures task time reductions achievable through software \emph{built on top of LLMs}, which is the dominant adoption channel in Latin America: direct chat-interface use lags OECD levels, but multinational firms operating in the region deploy LLM-augmented customer-relationship platforms, accounting tools, customer-service systems, and code assistants that workers use even when they do not interact with ChatGPT directly.

The post-COVID time window is a deliberate design choice: including pre-2020 periods would pool labor markets in two structurally different equilibria, violating the comparability requirement for the DiD control group. ChatGPT's launch delivers a single adoption date common to all occupations within a country; identification comes from within-occupation variation in how exposure interacts with the post-launch indicator. Baseline (2021) formality status is pre-registered as the paper's central within-country heterogeneity margin, on the argument that contemporaneous formality is itself an outcome of LLM exposure and therefore a bad control.

% RESULTS TBD - four narratives pre-registered, evaluated per country
The results are organized by four pre-committed narratives, each evaluated for every one of the seven countries. I state the narratives now and defer the quantitative headline numbers to \cref{sec:results}, where they appear with exposure-normalized effect sizes, confidence intervals, and Honest-DiD bounds for each country. \emph{Narrative A} (informality amplifies): country-level $|\hat\tau^c|$ exceeds two percent and is driven by the informal channel, with $\tau_I^c < \tau_F^c < 0$. \emph{Narrative B} (LAC--Denmark null replication): country-level effects are indistinguishable from zero in both channels. \emph{Narrative C} (null in formal, large in informal): $\tau_F^c \approx 0$ and $\tau_I^c$ is meaningfully negative, identifying a channel that Danish and US designs cannot detect because their informal sectors are negligible. \emph{Narrative D} (stratified gains): positive wage effects concentrate in tertiary-educated urban formal workers, bypassing the informal majority. Reporting which narrative each country supports turns cross-country heterogeneity from a robustness exercise into the central empirical contribution: seven independent tests of the same underlying mechanism.

We develop a stylized task-based framework in \cref{sec:theory} that organizes the predictions and connects them to the LAC formality channel.

The paper's cleanest contribution is its contrast with \citet{HumlumVestergaard2025_llm}. Denmark's combination of low informality, high digital readiness, strong worker bargaining, and generous social insurance is precisely the structural configuration most likely to mute a labor-market response. Latin America's configuration is the opposite -- high informality, fragmented wage-setting, weaker social insurance, and lower but non-trivial adoption -- and varies sharply across the seven countries. If the Danish null is universal, it should survive in every LAC country; if it reflects Danish institutions rather than LLM capabilities, the seven estimates should diverge in directions predictable from country-level formality and digital readiness.

The paper makes five contributions. First, it provides the first causal estimates of LLM exposure on labor-market outcomes for Latin America, filling the gap between the descriptive exposure literature \citep{Azuara2024_idb_ai, Ciaschi2025_distributive_ai, EganadelSol2025_ai_lac, WorldBank2024_genai_lac} and the OECD-focused causal literature \citep{HumlumVestergaard2025_llm, Hartley2024_labor_effects, Chen2025_llm_unemployment}. Second, it applies \citet{CallawayCGBS2024_continuous} continuous-treatment DiD to LLM exposure country by country; the prior causal literature has relied on binary cutoffs and has not exploited the seven-country comparison the LAC setting allows. Third, it elevates baseline formality from a subgroup check to the central within-country heterogeneity margin, with an imputation protocol that avoids using a post-treatment outcome as a conditioning variable. Fourth, it builds a reproducible seven-country harmonized crosswalk and dataset (2021--2025) that future LAC researchers can extend. Fifth, the paper pre-commits to four narratives before the analysis is run, so that the narrative emphasized for each country is determined by which empirical pattern obtains rather than by post-hoc specification search.

The rest of the paper proceeds as follows. \Cref{sec:literature} places the contribution in relation to the AI exposure literature, the post-ChatGPT causal evidence, the task-based theoretical framework, and the LAC-specific context. \Cref{sec:theory} develops the task-based theoretical framework that organizes the empirical predictions. \Cref{sec:method} presents the country-by-country identification strategy, the continuous-DiD estimating equation, the four pre-registered narratives, and the robustness layer. \Cref{sec:data} describes the seven harmonized country datasets. \Cref{sec:results} reports the country-by-country estimates and the within-country baseline-formality decompositions. \Cref{sec:robustness} presents the robustness evidence, and \Cref{sec:conclusion} discusses external validity and policy implications.
