\documentclass[12pt]{article}

\input{preambles/preamble}
\addbibresource{Bibliography_base.bib}

\title{The Labor Market Impact of Generative AI:\\ Causal Evidence from Latin America\thanks{Pontificia Universidad Cat\'{o}lica del Per\'{u} (PUCP), Programa Doctoral en Econom\'{i}a. Contact: \texttt{etorres@pucp.edu.pe}. I thank my advisors and the PUCP labor reading group for comments. This paper extends joint work with Oliver Azuara and Laura Ripani at the Inter-American Development Bank \citep{Azuara2024_idb_ai}. All errors are my own.}}

\author{Eric Torres}

\date{\today}

\begin{document}

\maketitle
\thispagestyle{empty}

\begin{abstract}
\noindent \singlespacing
ChatGPT's November 2022 launch hit labor markets everywhere on the same day. The careful causal estimates so far come almost entirely from OECD economies. This paper offers the first causal evidence on how large language model (LLM) exposure has reshaped employment, hours, and wages across six Latin American countries. I assemble harmonized labor force surveys for Costa Rica, Colombia, Ecuador, Mexico, Peru, and Uruguay (2021Q1--2025Q4), take the complementary-exposure score $\beta$ of \citet{Eloundou2023_gpt_exposure} as the treatment intensity, and estimate a continuous-treatment difference-in-differences specification country by country following \citet{CallawayCGBS2024_continuous}. The six country-specific estimates are the headline. Baseline (2021) formality is pre-registered as the central within-country heterogeneity margin. I contrast each country with the near-null Danish baseline of \citet{HumlumVestergaard2025_llm} and test four pre-committed narratives linking informality, adoption, and reallocation, country by country.

\vspace{1em}
\noindent \textbf{JEL Codes:} J23, J31, O33, O54, D63, L86

\vspace{0.5em}
\noindent \textbf{Keywords:} generative AI, large language models, labor demand, wage inequality, informality, Latin America, difference-in-differences
\end{abstract}

\newpage
\setcounter{page}{1}

\input{sections/introduction}
\input{sections/literature}
\input{sections/theoretical_framework}
\input{sections/methodology}
\input{sections/data}
\input{sections/results}
\input{sections/robustness}
\input{sections/conclusion}

\clearpage
\small \printbibliography

\end{document}
